Software Ticket Quality

### 2017-11-20 proposal/mprop.tex
Finish paper on fuzzy code linkage paper

\textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to find an approach that improves on
    previous methods to link source code fragments in discussions to source code.
    These previous methods were mainly based on information retrieval or 
    change log analysis.
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

>>>>

\textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to find an approach that improves on
    previous methods to link source code fragments in discussions to source code.
    These previous methods were mainly based on information retrieval or 
    change log analysis. The main reason behind the authors' goal was
    that a successful tool which could accomplish the goal would drastically
    improve traceability in a project.
  \item \textbf{What was the method?}
    They created a tool based on fuzzy code search that could parse bug reports
    discussions and, then, match the locations in the source code where those
    code fragments belong to. The authors conducted the evaluation on the Eclipse
    open source project after developing the 2 stages of the algorithm:
      \begin{itemize}
        \item they first use infoZilla, presented in \cite{bettenburg2008extracting},
        to extract source code from documents belonging to a document archive;
        \item then they perform a fuzzy textual search using a token-based clone
        detection tool;
        \item finally, they analyze all clone groups that associate clone pairs with
        extracted code fragments to source code files; then, a traceability link is created,
        which is basically a tuple containing a clone group ID and file paths corresponding
        to the corresponding source code files.
      \end{itemize}
  \item \textbf{What did they learn?}
    First of all, as many software projects have large code bases, creating such 
    traceability links is no trivial task. Moreover, they noticed an increase of 20.01\%
    in total traceability links between issue reports and source code compared to state of the art
    technique (which is also most used one), change log analysis. Thus, there is room for
    improvement in this area.
  \item \textbf{Relevance to our work}:
    If we'd decide to use this approach, we can find out even more information about
    quality in issue reports/tickets as we can also analyze the source code files necessary
    to fix that specific issue. This, combined with infoZilla, could prove valuable for our
    mining and extraction processes.
\end{itemize}
